Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-28 paper.tex
adds a list of possible related work papers

\begin{itemize}
  \item Trajectories visualization
  \item Differences -- ligand MD trajectory, waters
  \item Missing?
\end{itemize}

>>>>

\begin{itemize}
	\item General molecular vis:
		\begin{itemize}
			\item Visual Analysis of Biomolecular Cavities: State of the Art
			\item Visualization of biomolecular structures: State of the art revisited.
		\end{itemize}
  	\item Trajectories visualization
  		\begin{itemize}
  			\item Interactive Visual Analysis of Families of Function Graphs
  			\item Curve Boxplot: Generalization of Boxplot for Ensembles of Curves
  			\item Streamline Variability Plots for Characterizing the Uncertainty in Vector Field Ensembles
  			\item {\color{red} simplifikace ve 3D, maybe not related} SimpliFly: A Methodology for Simplification and Thematic Enhancement of Trajectories
  			\item Generalized box-plot for root growth ensembles
  		\end{itemize}
  	\item relevant for the modulate 3D visualization
  		\begin{itemize}
  			\item Game On, Science - How Video Game Technology May Help Biologists Tackle Visualization Challenges
  		\end{itemize}
  	\item relevant for density visualization
  		\begin{itemize}
  			\item Spatial Generalization and Aggregation of Massive Movement Data
  			\item Space–time density of trajectories: exploring spatio-temporal patterns in movement data
  		\end{itemize}
  	\item relevant for selection by density
  		\begin{itemize}
  			\item Visualizing Dynamical Systems near Critical Points
  			\item Strategies for Interactive Exploration of 3D Flow Using Evenly-Spaced Illuminated Streamlines
  		\end{itemize}
  	\item Trajectories in molecular context
  		\begin{itemize}
  			\item Watergate: Visual Exploration of Water Trajectories in Protein Dynamics
			\item Interactive Exploration of Ligand Transportation through Protein Tunnels
  			\item MolPathFinder: Interactive Multi-Dimensional Path Filtering of Molecular Dynamics Simulation Data
  			\item {\color{red}not completely relevant} Methodologies for the Analysis of Instantaneous Lipid Diffusion in MD Simulations of Large Membrane Systems
  			\item {\color{red}maybe not relevant} Heterogeneity-based Guidance for Exploring Multiscale Data in Systems Biology
			\item {\color{red}water trajectories - 3D} Visual Abstractions of Solvent Pathlines near Protein Cavities
			\item {\color{red}water trajectories - 3D - domain paper} Tracking the Flow of Water through Photosystem II Using Molecular
			\item {\color{red}water trajectories - 3D - domain paper - visualization by pymol} AQUA-DUCT: a ligands tracking tool Dynamics and Streamline Tracing
  		\end{itemize}
  \item Missing?
\end{itemize}
